\documentclass{resume} % Use the custom resume.cls style]{article}

%-----------------------------------------------------------
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{hyperref}
\usepackage{framed}
\usepackage{tocloft}
\usepackage{bibentry}
\usepackage{indentfirst}
\usepackage{setspace}
\usepackage{ulem}
\usepackage{indentfirst}
\usepackage{geometry}
\usepackage{paralist}
\usepackage{enumitem}
\setenumerate{itemsep=0pt,partopsep=0pt,parsep=\parskip,topsep=0pt}
\setitemize{itemsep=0pt,partopsep=0pt,parsep=\parskip,topsep=0pt}
\setdescription{itemsep=0pt,partopsep=0pt,parsep=\parskip,topsep=0pt}
\let\itemize\compactitem
\let\enditemize\endcompactitem
\let\enumerate\compactenum
\let\endenumerate\endcompactenum
\let\description\compactdesc
\let\enddescription\endcompactdesc


\hypersetup{
    colorlinks,%
    citecolor=black,%
    filecolor=black,%
    linkcolor=black,%
    urlcolor=mygreylink     % can put red here to better visualize the links
}
\urlstyle{same}
\definecolor{mygrey}{gray}{.85}
\definecolor{mygreylink}{gray}{.30}
\textheight=9.0in
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{0.375in}
\addtolength{\textwidth}{0.5in}
\addtolength{\topmargin}{-.375in}
\addtolength{\textheight}{0.75in}

%-----------------------------------------------------------
%Custom commands

\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		#3 & #4 \\
\end{tabular*}\vspace{-6pt}}

\newcommand{\newressubheading}[2]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
\end{tabular*}\vspace{-6pt}}

\newcommand{\mywebheader}{
\begin{tabular*}{7in}{c@{\extracolsep{\fill}}r}	
%\textbf{{\LARGE Yu Haomiao}}\\
%\href{mailto:1518948547@qq.com}{1518948547@qq.com}\\
%\href{http://home.ustc.edu.cn/~ryanyang}{http://home.ustc.edu.cn/$\sim$ryanyang} \\
\end{tabular*}
\\
\vspace{-5pt}}
%-----------------------------------------------------------

%-----------------------------------------------------------
%General Resume Tips
%   No periods!  Technically, nothing in this document is a full sentence.
%   Use parallelism by ending key words with the same thing,  i.e. "Coordinated; Designed; Communicated".
%   More tips on bottom of this LaTeX document.
%-----------------------------------------------------------


\geometry{left=1cm,right=1cm,top=1cm,bottom=1cm}

\begin{document} \small
\begin{spacing}{1}
\vspace{-0.5in}

\begin{center}
\begin{tabular}{*{11}{c}}
    \vspace{-9pt}
    \textbf{\Huge{Dongtai Du}}\\\\
    {\footnotesize Apt 951,185 Freeman Street, Brookline, MA02446, US} \\
    {\footnotesize phone:(857)600-9260} \hspace{1cm} {\footnotesize {https://dudongtai2002.github.io}}\hspace{1cm}{\footnotesize {Email:dudongtai2002@gmail.com}} \\
\end{tabular}

\uline{{\bf{\LARGE Education}}\hfill{\hspace{15cm}{}}} \\
\vspace{1mm}
{\bf Boston University \hspace{3cm} } \hfill {Aug.2014 - May.2016} \\
\hspace{3cm}
\hspace{-6.3cm}{M.S. in Computer Engineering:\hspace{1.68cm}Computer Networks, Operating System, Analysis of Algorithms,}\\
\hspace{3.3cm}{Advanced Data Structure, Cloud Computing, Machine Learning}\\
{\bf University of Science and Technology of China(USTC) \hspace{1.7cm} } \hfill {Sept.2010 - Jun.2014}\\
\hspace{-17.2cm}{B.S. in Physics} \hspace{1.66cm}\\


\vspace{4mm}

\uline{{\bf{\LARGE Working Experience}}\hfill{\hspace{10cm}{}}} \\
\vspace{1mm}
{\bf Sogou Inc.} \hfill {\small Beijing, Dec.2015 - Jan.2016} \\
\hspace{-15cm}{Software Development Intern}
\vspace{-2mm}
\begin{itemize}
\item{Rebuilt a Dynamic Link Library(DLL) for Sogou Pinyin using C++, which could uniquely identify a PC using MD5 to generate a 16 byte serial number based on hardware information. Reduced the error rate from 3\%\ to 0.1\%\ .}\\
\vspace{0.3mm}
\item{Followed Agile project management and deployed my module using Tortoise SVN.}\\
\vspace{1mm}
    \hspace{-10.0mm}\textit{Environment: Windows Desktop development, C++, Visual Studio.}
\end{itemize}
{\bf Boston University College of Engineering } \hfill {\small Boston, Feb.2016 - May.2016} \\
\hspace{-16.6cm}{Teaching Assistant}
\vspace{-2mm}
\begin{itemize}
\item{ Lab assistant \&\ grader for EC512: Enterprise Client/Server Software. C\#\ , Asp.Net development. Helped answer all the questions from students and set up test case for homework assignments(80 assignments per week).}\\

\end{itemize}
\vspace{-1mm}
\vspace{2.5mm}
\uline{{\bf{\LARGE Projects}}\hfill{\hspace{10cm}{}}} \\
\vspace{2mm}	
{\bf Cloud-Computing - OpenStack Pass-Through Service } \hfill {\small Boston, Feb.2015 - May.2015} \\
\vspace{0.1mm}
\begin{itemize}
\item{Wrote a web application that allows cloud users to leverage 3 different Openstack services from various providers
.} \\
\item{Establish a proxy server between the client and the Openstack platform on Linux using python Flask } \\

\hspace{-10.0mm}\textit{Environment: Linux, Python,  Html/CSS, OpenStack API, Http programming.}
\vspace{-1mm}
\end{itemize}
\vspace{0mm}
\vspace{1.7mm}
{\bf Extension of Google Map - MapApp} \hfill {\small  Boston, Sept.2015 - Dec.2015} \\
\vspace{0.1mm}
\begin{itemize}
\item{Build a wet application on Amazon EC2 Linux Server with a data-set containing 2,000,000 coordinates. It displays a map of US and support range search and nearest neighbor search. JavaScript and JQuery \&\ Ajax for the frontend.} \\
\item{Implemented K-D Tree based backend in java, reduce time complexity from O(n) to O(lgn).  } \\
\hspace{-10.0mm}\textit{Environment: Linux, Apache Tomcat, Java, JavaScript, JQuery.}
\vspace{-2mm}
\end{itemize}
\vspace{2.4mm}
{\bf Machine Learning - AlFont} \hfill {\small Boston, Mar.2016 - May.2016} \\
\vspace{0.1mm}
\begin{itemize}
\item{Implemented two multi-layer convolution neural networks that are able to learn, identify and generate characters in specific font. Collected and generated characters as training data using over 10,000 fonts. Trained the network using mini-batch gradient descent and achieved an accruancy rate over 90\%\ . } \\
\item{Led a four members team. Allocated 4 roles: Team leader, front-end \&\ documentation, back-end, R\&\ D. Set milestones and assign work in detail for each member.} \\
\hspace{-10.0mm}\textit{Environment: Python Numpy $\&$ Theano library, Matlab script.}
\vspace{-1mm}
\end{itemize}
\vspace{1.8mm}
{\bf Ios Calculator} \hfill {\small Boston, Sep.2016} \\
\vspace{0.1mm}
\begin{itemize}
\item{Built and deployed a calculator on ios, supporting all basic arithmetic operations for multiple screen size iphone/ipads. } \\
\item{Applied MVC design pattern. } \\
\hspace{-10.0mm}\textit{Environment: Xcode, Swift 3.}
\vspace{-1mm}
\end{itemize}
\vspace{1.9mm}
{\bf Web Development of User Management System} \hfill {\small  Boston, Apr.2015} \\
\vspace{0.1mm}
\begin{itemize}
\item{Used Asp.NET Web Form and C\#\ to develop a full stack website which allows users to register, maintain and modify their own account and check out part of other user’s information.} \\
\item{Implemented the website's service logic including cookie, session state, database connectivity, security requirement, and authentication of clients.} \\
\hspace{-10.0mm}\textit{Environment: C\#\ , Asp.Net, Html/CSS, SQL server.}
\vspace{-1mm}
\end{itemize}

\vspace{3mm}

\uline{{\bf{\LARGE Technical Skills}}\hfill{\hspace{10cm}{}}} \\
\vspace{1mm}
\hspace{-6.0cm}{\bf Languages:} \hspace{2cm} {C, C++,  C\#\ , Java, JavaScript, Html/ CSS, Python, Swift.} \\
\hspace{-5.85cm}{\bf Environment:} \hspace{1.55cm} {Windows32 Desktop, Linux, Asp.NET, Apache Tomcat, IOS. } \\


\end{center}
\end{spacing}
\end{document}

%%%%%%%%%%%%%%%%%%%%% 